### 2024-05-31 2024-5-13/sections/heuristic.tex
section 7.2

In Section~\ref{sec:algorithm}, to deal with the non-register-representable RECL constraints, we unfold all the non-register-representable occurrences of counting operators. Nevertheless, 
the naive unfolding incurs an exponential blow-up over the formula sizes, especially when the counting bounds are large. 
Recall that an occurrence of counting operators is said to be non-register-representable if it is in the scope of some Kleene star, another counting operator, complement, or language difference. Since Kleene star can be seen as a special case of the counting operators, and language difference $e_1 \setminus e_2$ can be rewritten as $e_1 \cap \overline{e_2}$, without loss of generality, we can assume that a non-register representable occurrence of a  counting operator is in the scope of another counting operator or some complement operator. 
In the sequel, to alleviate the formula-size blow-up problem resulted from the naive unfolding, we present various optimizations, for the nesting of counting operators and the nesting of a counting operator and a complement operator respectively. 
% two situations that a counting operator is in the scope of another counting operator and in the scope of a complement operator respectively.

@@

\subsection{Optimizations for the nesting of a counting operator and a complement operator}
As we mentioned in the above section \ref{heuristic:nested}, the unwinding process of the complement operator is exponential to the counting bounds in the worst case. We present a heuristic to reduce the number of states generated by the unwinding process. The idea is to under-approximate and over-approximate the language of the regex first, so that we can avoid unwinding counting operators in complement. We present the heuristic in the following algorithm.

\medskip
\noindent
\emph{Step 1. (Under-approximate the language of the regex with complement operators).}

The under-approximation is replacing each counting operator in the subregex of complement with a Kleene star operator. The language of the subregex is a superset of the language of it after under-approximation. In sequential, the complement of the subregex is a subset of origin. Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement. For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.

>>>>

In Section~\ref{sec:algorithm}, to deal with the non-register-representable RECL constraints, we unfold all the non-register-representable occurrences of counting operators. Nevertheless, 
the naive unfolding incurs an exponential blow-up over the formula sizes, especially when the counting bounds are large. 
Recall that an occurrence of counting operators is said to be non-register-representable if it is in the scope of some Kleene star, another counting operator, complement, or language difference. Since Kleene star can be seen as a special case of the counting operators, and language difference $e_1 \setminus e_2$ can be rewritten as $e_1 \cap \overline{e_2}$, without loss of generality, we can assume that a non-register representable occurrence of a  counting operator is in the scope of another counting operator or some complement operator. 
In the sequel, to alleviate the formula-size blow-up problem resulted from the naive unfolding, we present various optimizations, for the nesting of counting operators and the nesting of  counting operators and a complement operator respectively. 
% two situations that a counting operator is in the scope of another counting operator and in the scope of a complement operator respectively.

@@

\subsection{Optimizations for the nesting of counting operators and a complement operator}

As mentioned in Section~\ref{sec:algorithm}, if some counting operators are in the scope of a complement operator, it is necessary to unfold these counting operators before the complement operation. The exponential blow-up in the unfolding combined with the blow-up in the complement operation will produce huge number of states.  To alleviate this problem, we propose two approximations of the complement operation, i.e. an under-approximation and an over-approximation, and combine them into a procedure that achieves a nice balance between efficiency and precision.

Let $e = \overline{e_1}$ be a regular expression, where $e_1$ is a register-representable regular expression.

\paragraph*{Under approximation}
%
One way of doing the complement operation is to transform $e_1$ into a regular expression that does not contain counting operators. We compute an under-approximation of $e$ by replacing each occurrence of the counting operators in $e_1$, say $(e_2)^{\{m,n\}}$ or $(e_2^{\{n, \infty\}})$, by $e_2^*$. Let us use $e'_1$ denote the resulting regular expression. Note that $e'_1$ does not contain counting operators. Moreover, it is easy to observe that $\Lang(e_1) \subseteq \Lang(e'_1)$. As a result, we have $\Lang(\overline{e'_1}) \subseteq \Lang(\overline{e_1})$. That is, $\overline{e'_1}$ is an under-approximation of $\overline{e_1}$.

%The under-approximation is replacing each counting operator in the subregex of complement with a Kleene star operator. The language of the subregex is a superset of the language of it after under-approximation. In sequential, the complement of the subregex is a subset of origin. Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement. For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.

%As we mentioned in the above section \ref{heuristic:nested}, the unwinding process of the complement operator is exponential to the counting bounds in the worst case. We present a heuristic to reduce the number of states generated by the unwinding process. The idea is to under-approximate and over-approximate the language of the regex first, so that we can avoid unwinding counting operators in complement. We present the heuristic in the following algorithm.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hide{
\medskip
\noindent
\emph{Step 1. (Under-approximate the language of the regex with complement operators).}

The under-approximation is replacing each counting operator in the subregex of complement with a Kleene star operator. The language of the subregex is a superset of the language of it after under-approximation. In sequential, the complement of the subregex is a subset of origin. Note that this approach only works for non-nested complement, which means there is no other complement operators in the complement. For nested complement,  we naively handle the inner complement operators as paper \cite{Denghang2023} and then under-approximate the outer complement operator.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
